### 2023-01-20 code/1_exclusions/1_exclusionsCN.Rmd
cogsci paper exchange

df.ppts_not_finished_M <- df.resp_M %>% 
  group_by(subject) %>%
  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
  filter(finished == "no")

@@

df.ppts_att_M <- df.resp_M %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "选择")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent >= 0.8)

df.resp_M <- df.resp_M %>%
  filter(subject %in% df.ppts_att_M$subject)

ppts_resp_M <- unique(df.resp_M$subject)
```

@@

ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #3
percent_dropped = length(intersect(ppts_non_native_lang_M, ppts_resp_M)) / length(ppts_resp_M)
percent_dropped #0.01086

#fluent in Vietnamese & Mandarin
df.lang_sp_vi_M <- df.demog %>%
  filter(demog_question == "lang_sp_vi" & demog_response > 4)

df.lang_ud_vi_M <- df.demog %>%
  filter(demog_question == "lang_ud_vi" & demog_response > 4)

@@

ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #1
percent_dropped = length(intersect(ppts_vi_speaker_M, ppts_resp_M)) / length(ppts_resp_M)
percent_dropped #0

df.lang_sp_en_M <- df.demog %>%
  filter(demog_question == "lang_sp_en" & demog_response > 4)

df.lang_ud_en_M <- df.demog %>%
  filter(demog_question == "lang_ud_en" & demog_response > 4)

@@

ppts_en_speaker_M = unique(df.lang_en_M$subject) #74
percent_dropped = length(intersect(ppts_en_speaker_M, ppts_resp_M)) / length(ppts_resp_M)
percent_dropped #0.375 # do not use this criterion

@@

ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #40
percent_dropped = length(intersect(ppts_lived_abroad_M, ppts_resp_M)) / length(unique(df.resp_M$subject))
percent_dropped #0.163043

@@

ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #12
percent_dropped = length(intersect(ppts_oversea_exp_M, ppts_resp_M)) / length(unique(df.resp_M$subject))
percent_dropped #0.0434782

df.resp_M <- df.resp_M %>%
  filter(!(subject %in% ppts_non_native_lang_M),
         !(subject %in% ppts_vi_speaker_M), 
         !(subject %in% ppts_lived_abroad_M), 
         !(subject %in% ppts_oversea_exp_M))

length(unique(df.resp_M$subject)) #149
```

```{r}
write.csv(df.resp_M, "../../data/responding/dataCN_excl.csv")
```

>>>>

df.ppts_not_finished_M <- df.resp_M %>% #3
  group_by(subject) %>%
  summarize(finished = ifelse("demo-final" %in% unique(variable_type), "yes", "no")) %>%
  filter(finished == "no")

@@

df.ppts_att_M <- df.resp_M %>% #166
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "选择")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent == 1.0)

df.resp_M_aft_attn <- df.resp_M %>% #38841
  filter(subject %in% df.ppts_att_M$subject)

ppts_resp_M_aft_attn <- unique(df.resp_M$subject)
```

@@

ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #3
percent_dropped = length(intersect(ppts_non_native_lang_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
percent_dropped #0.01086

#fluent in Vietnamese & Mandarin
df.lang_sp_vi_M <- df.demog %>%
  filter(demog_question == "lang_sp_vi" & as.numeric(demog_response) > 4)

df.lang_ud_vi_M <- df.demog %>%
  filter(demog_question == "lang_ud_vi" & as.numeric(demog_response) > 4)

@@

ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #1
percent_dropped = length(intersect(ppts_vi_speaker_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
percent_dropped #0

df.lang_sp_en_M <- df.demog %>%
  filter(demog_question == "lang_sp_en" & as.numeric(demog_response) > 4)

df.lang_ud_en_M <- df.demog %>%
  filter(demog_question == "lang_ud_en" & as.numeric(demog_response) > 4)

@@

ppts_en_speaker_M = unique(df.lang_en_M$subject) #74
percent_dropped = length(intersect(ppts_en_speaker_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
percent_dropped #0.375 # do not use this criterion

@@

ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #40
percent_dropped = length(intersect(ppts_lived_abroad_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
percent_dropped #0.163043

@@

ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #12
percent_dropped = length(intersect(ppts_oversea_exp_M, ppts_resp_M_aft_attn)) / length(ppts_resp_M_aft_attn)
percent_dropped #0.0434782

df.resp_M_aft_demog <- df.resp_M_aft_attn %>%
  filter(!(subject %in% ppts_non_native_lang_M),
         !(subject %in% ppts_vi_speaker_M), 
         !(subject %in% ppts_lived_abroad_M), 
         !(subject %in% ppts_oversea_exp_M))

length(unique(df.resp_M_aft_demog$subject)) #132
```

```{r}
df.demog_metadata <- data.frame(
  country = c("China"),
  ppts_finished = c(length(unique(df.ppts_finished_M$subject))),
  ppts_att_check_excl = c(length(unique(df.ppts_finished_M$subject)) - length(unique(df.ppts_att_M$subject))), 
  ppts_after_att_check_excl = c(length(unique(df.ppts_att_M$subject))),
  ppts_non_native_speaker = c(paste(length(ppts_non_native_lang_M),"*")), 
  ppts_en_speaker = c(length(ppts_en_speaker_M)), 
  ppts_vi_speaker = c(paste(length(ppts_vi_speaker_M),"*")),
  ppts_zh_speaker = c("N/A"), 
  ppts_lived_abroad = c(paste(length(ppts_lived_abroad_M),"*")), 
  ppts_oversea_exp = c(paste(length(ppts_oversea_exp_M), "*")),
  ppts_after_demog_excl = c(length(unique(df.resp_M_aft_demog$subject))))
```

```{r}
write.csv(df.resp_M_aft_demog, "../../data/responding/dataCN_excl.csv")
write.csv(df.demog_metadata, "../../data/responding/dataCN_excl_metadata.csv")
```

### 2023-01-20 code/1_exclusions/1_exclusionsUS.Rmd
cogsci paper exchange

df.ppts_att_E <- df.resp_E %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Choose ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent >= 0.8)

df.resp_E <- df.resp_E %>%
  filter(subject %in% df.ppts_att_E$subject)

ppts_resp_E <- unique(df.resp_E$subject)
```

```{r}
df.demog <- read.csv("../../data/responding/data_demog.csv") %>%
  select(-X) %>%
  filter(country == "US")
```

@@

ppts_non_native_lang_E = unique(df.ppts_non_native_lang_E$subject)#20
percent_dropped = length(intersect(ppts_non_native_lang_E, ppts_resp_E)) / length(ppts_resp_E)
percent_dropped #0.104166

#fluent in Vietnamese & Mandarin
df.lang_sp_vi_E <- df.demog %>%
  filter(demog_question == "lang_sp_vi" & demog_response > 4)

df.lang_ud_vi_E <- df.demog %>%
  filter(demog_question == "lang_ud_vi" & demog_response > 4)

@@

ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #2
percent_dropped = length(intersect(ppts_vi_speaker_E, ppts_resp_E)) / length(ppts_resp_E)
percent_dropped #0.01041666

df.lang_sp_zh_E <- df.demog %>%
  filter(demog_question == "lang_sp_zh" & demog_response > 4)

df.lang_ud_zh_E <- df.demog %>%
  filter(demog_question == "lang_ud_zh" & demog_response > 4)

@@

ppts_zh_speaker_E = unique(df.lang_zh_E$subject) #30
percent_dropped = length(intersect(ppts_zh_speaker_E, ppts_resp_E)) / length(ppts_resp_E)
percent_dropped #0.15104

@@

ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #36
percent_dropped = length(intersect(ppts_lived_abroad_E, ppts_resp_E)) / length(unique(df.resp_E$subject))
percent_dropped #0.171875

@@

ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #95
percent_dropped = length(intersect(ppts_oversea_exp_E, ppts_resp_E)) / length(unique(df.resp_E$subject))
percent_dropped #0.4739 # will not use this criterion

df.resp_E <- df.resp_E %>%
  filter(!(subject %in% ppts_non_native_lang_E),
         !(subject %in% ppts_vi_speaker_E), 
         !(subject %in% ppts_zh_speaker_E),
         !(subject %in% ppts_lived_abroad_E))

length(unique(df.resp_E$subject)) #124
```

```{r}
write.csv(df.resp_E, "../../data/responding/dataUS_excl.csv")
```

>>>>

df.ppts_att_E <- df.resp_E %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Choose ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent == 1.0)

df.resp_E_aft_attn <- df.resp_E %>%
  filter(subject %in% df.ppts_att_E$subject)

ppts_resp_E_aft_attn <- unique(df.resp_E_aft_attn$subject)
```

```{r}
df.demog <- read.csv("../../data/responding/data_demog.csv") %>%
  select(-X) %>%
  filter(country == "US") %>%
  filter(subject %in% ppts_resp_E_aft_attn)
```

@@

ppts_non_native_lang_E = unique(df.ppts_non_native_lang_E$subject)#20
percent_dropped = length(intersect(ppts_non_native_lang_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
percent_dropped #0.1034483

#fluent in Vietnamese & Mandarin
df.lang_sp_vi_E <- df.demog %>%
  filter(demog_question == "lang_sp_vi" & as.numeric(demog_response) > 4)

df.lang_ud_vi_E <- df.demog %>%
  filter(demog_question == "lang_ud_vi" & as.numeric(demog_response) > 4)

@@

ppts_vi_speaker_E = unique(df.lang_vi_E$subject) #2
percent_dropped = length(intersect(ppts_vi_speaker_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
percent_dropped #0.01149425

df.lang_sp_zh_E <- df.demog %>%
  filter(demog_question == "lang_sp_zh" & as.numeric(demog_response) > 4)

df.lang_ud_zh_E <- df.demog %>%
  filter(demog_question == "lang_ud_zh" & as.numeric(demog_response) > 4)

@@

ppts_zh_speaker_E = unique(df.lang_zh_E$subject) #30
percent_dropped = length(intersect(ppts_zh_speaker_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
percent_dropped #0.1436782

@@

ppts_lived_abroad_E = unique(df.lived_abroad_E$subject) #36
percent_dropped = length(intersect(ppts_lived_abroad_E, ppts_resp_E_aft_attn)) / length(ppts_resp_E_aft_attn)
percent_dropped #0.166667

@@

ppts_oversea_exp_E = unique(df.oversea_exp_E$subject) #95
percent_dropped = length(intersect(ppts_oversea_exp_E, ppts_resp_E_aft_attn)) / length(unique(df.resp_E_aft_attn$subject))
percent_dropped #0.4425287 # will not use this criterion

df.resp_E_aft_demog <- df.resp_E_aft_attn %>%
  filter(!(subject %in% ppts_non_native_lang_E),
         !(subject %in% ppts_vi_speaker_E), 
         !(subject %in% ppts_zh_speaker_E),
         !(subject %in% ppts_lived_abroad_E))

length(unique(df.resp_E_aft_demog$subject)) #124

```{r}
df.demog_metadata <- data.frame(
  country = c("US"),
  ppts_finished = c(length(unique(df.ppts_finished_E$subject))),
  ppts_att_check_excl = c(length(unique(df.ppts_finished_E$subject)) - length(unique(df.ppts_att_E$subject))), 
  ppts_after_att_check_excl = c(length(unique(df.ppts_att_E$subject))),
  ppts_non_native_speaker = c(paste(length(ppts_non_native_lang_E),"*")), 
  ppts_en_speaker = c("N/A"),
  ppts_vi_speaker = c(paste(length(ppts_vi_speaker_E),"*")), 
  ppts_zh_speaker = c(paste(length(ppts_zh_speaker_E),"*")), 
  ppts_lived_abroad = c(paste(length(ppts_lived_abroad_E),"*")), 
  ppts_oversea_exp = c(length(ppts_oversea_exp_E)),
  ppts_after_demog_excl = c(length(unique(df.resp_E_aft_demog$subject))))
# colnames(df.demog_metadata) <- c("Participants Finished", 
#                                  "Participants ")
```

```{r}
write.csv(df.resp_E_aft_demog, "../../data/responding/dataUS_excl.csv")
write.csv(df.demog_metadata, "../../data/responding/dataUS_excl_metadata.csv")
```

### 2023-01-20 code/1_exclusions/1_exclusionsVN.Rmd
cogsci paper exchange

df.ppts_att_V <- df.resp_V %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Chọn ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent >= 0.8)

df.resp_V <- df.resp_V %>%
  filter(subject %in% df.ppts_att_V$subject) #73

ppts_resp_V <- unique(df.resp_V$subject) #137
```

@@

ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)#2
percent_dropped = length(intersect(ppts_non_native_lang_V, ppts_resp_V)) / length(ppts_resp_V)
percent_dropped #0

#fluent in Vietnamese & Mandarin
df.lang_sp_en_V <- df.demog %>%
  filter(demog_question == "lang_sp_en" & demog_response > 4)

df.lang_ud_en_V <- df.demog %>%
  filter(demog_question == "lang_ud_en" & demog_response > 4)

@@

ppts_en_speaker_V = unique(df.lang_en_V$subject) #119
percent_dropped = length(intersect(ppts_en_speaker_V, ppts_resp_V)) / length(ppts_resp_V)
percent_dropped #0.6277 # do not use this criterion

df.lang_sp_zh_V <- df.demog %>%
  filter(demog_question == "lang_sp_zh" & demog_response > 4)

df.lang_ud_zh_V <- df.demog %>%
  filter(demog_question == "lang_ud_zh" & demog_response > 4)

@@

ppts_zh_speaker_V = unique(df.lang_zh_V$subject) #9
percent_dropped = length(intersect(ppts_zh_speaker_V, ppts_resp_V)) / length(ppts_resp_V)
percent_dropped #0.05839416

@@

ppts_lived_abroad_V = unique(df.lived_abroad_V$subject) #18
percent_dropped = length(intersect(ppts_lived_abroad_V, ppts_resp_V)) / length(unique(df.resp_V$subject))
percent_dropped #0.05839416

#have travelled extensively (more than 6 international experiences of 2 days or longer)
df.oversea_exp_V <- df.demog %>%
  filter(demog_question == "overseaexpnum" & demog_response == "Six or more experiences")

ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #95
percent_dropped = length(intersect(ppts_oversea_exp_V, ppts_resp_V)) / length(unique(df.resp_V$subject))
percent_dropped #0.4739 # will not use this criterion

df.resp_V <- df.resp_V %>%
  filter(!(subject %in% ppts_non_native_lang_V),
         !(subject %in% ppts_vi_speaker_V), 
         !(subject %in% ppts_zh_speaker_V),
         !(subject %in% ppts_lived_abroad_V))

length(unique(df.resp_V$subject)) #124
```

```{r}
write.csv(df.resp_V, "../../data/responding/dataVN_excl.csv")
```

>>>>

df.ppts_att_V <- df.resp_V %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "Chọn ")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent == 1.0)

df.resp_V_aft_attn <- df.resp_V %>%
  filter(subject %in% df.ppts_att_V$subject) #73

ppts_resp_V_aft_attn <- unique(df.resp_V$subject) #137
```

@@

ppts_non_native_lang_V = unique(df.ppts_non_native_lang_V$subject)#2
percent_dropped = length(intersect(ppts_non_native_lang_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
percent_dropped #0.01

#fluent in Vietnamese & Mandarin
df.lang_sp_en_V <- df.demog %>%
  filter(demog_question == "lang_sp_en" & as.numeric(demog_response) > 4)

df.lang_ud_en_V <- df.demog %>%
  filter(demog_question == "lang_ud_en" & as.numeric(demog_response) > 4)

@@

ppts_en_speaker_V = unique(df.lang_en_V$subject) #127
percent_dropped = length(intersect(ppts_en_speaker_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
percent_dropped #0.6277 # do not use this criterion

df.lang_sp_zh_V <- df.demog %>%
  filter(demog_question == "lang_sp_zh" & as.numeric(demog_response) > 4)

df.lang_ud_zh_V <- df.demog %>%
  filter(demog_question == "lang_ud_zh" & as.numeric(demog_response) > 4)

@@

ppts_zh_speaker_V = unique(df.lang_zh_V$subject) #9
percent_dropped = length(intersect(ppts_zh_speaker_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
percent_dropped #0.04522613

@@

ppts_lived_abroad_V = unique(df.lived_abroad_V$subject) #18
percent_dropped = length(intersect(ppts_lived_abroad_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
percent_dropped #0.05839416

#have travelled extensively (more than 6 international experiences of 2 days or longer)
df.oversea_exp_V <- df.demog %>%
  filter(demog_question == "overseaexpnum" & demog_response == "6 lần trở lên")

ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #20
percent_dropped = length(intersect(ppts_oversea_exp_V, ppts_resp_V_aft_attn)) / length(ppts_resp_V_aft_attn)
percent_dropped #0.109

df.resp_V_aft_demog <- df.resp_V_aft_attn %>%
  filter(!(subject %in% ppts_non_native_lang_V),
         !(subject %in% ppts_zh_speaker_V),
         !(subject %in% ppts_lived_abroad_V), 
         !(subject %in% ppts_oversea_exp_V))

length(unique(df.resp_V_aft_demog$subject)) #110
```

```{r}
df.demog_metadata <- data.frame(
  country = c("Vietnam"),
  ppts_finished = c(length(unique(df.ppts_finished_V$subject))),
  ppts_att_check_excl = c(length(unique(df.ppts_finished_V$subject)) - length(unique(df.ppts_att_V$subject))), 
  ppts_after_att_check_excl = c(length(unique(df.ppts_att_V$subject))),
  ppts_non_native_speaker = c(paste(length(ppts_non_native_lang_V),"*")), 
  ppts_en_speaker = c(paste(length(ppts_en_speaker_V))), 
  ppts_vi_speaker = c("N/A"),
  ppts_zh_speaker = c(paste(length(ppts_zh_speaker_V),"*")), 
  ppts_lived_abroad = c(paste(length(ppts_lived_abroad_V),"*")), 
  ppts_oversea_exp = c(paste(length(ppts_oversea_exp_V), "*")),
  ppts_after_demog_excl = c(length(unique(df.resp_V_aft_demog$subject))))
```

```{r}
write.csv(df.resp_V_aft_demog, "../../data/responding/dataVN_excl.csv")
write.csv(df.demog_metadata, "../../data/responding/dataVN_excl_metadata.csv")
```

### 2023-01-20 code/1_exclusions_old/1_exclusionsCN.Rmd
cogsci paper exchange

df.ppts_att_M <- df.resp_M %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "选择")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent == 1.0)

df.resp_M <- df.resp_M %>%
  filter(subject %in% df.ppts_att_M$subject) 
```

@@

df.ppts_non_native_lang_M <- df.resp_M %>%
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language") %>%
  mutate(native_speaker = get_native_lang(responses)) %>%
  filter(native_speaker == "不是")

ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #2
percent_dropped = length(ppts_non_native_lang_M) / length(unique(df.resp_M$subject))
percent_dropped #0.01398601

@@

ppts_en_speaker_M = unique(df.lang_en_M$subject) #50
percent_dropped = length(ppts_en_speaker_M) / length(unique(df.resp_M$subject))
percent_dropped #0.3496503 # will not use this criterion

@@

ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #50
percent_dropped = length(ppts_vi_speaker_M) / length(unique(df.resp_M$subject))
percent_dropped #0

@@

ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #23
percent_dropped = length(ppts_lived_abroad_M) / length(unique(df.resp_M$subject))
percent_dropped # 0.1608392

@@

ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #0
percent_dropped = length(ppts_oversea_exp_M) / length(unique(df.resp_M$subject))
percent_dropped #0

@@

length(unique(df.resp_M$subject)) 
```

>>>>

df.ppts_att_M <- df.resp_M %>% #166
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "选择")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent == 1.0)

df.resp_M <- df.resp_M %>% #38841
  filter(subject %in% df.ppts_att_M$subject) 
```

@@

df.ppts_non_native_lang_M <- df.resp_M %>% #2
  select(subject, responses, variable_type) %>%
  filter(variable_type == "demog_language") %>%
  mutate(native_speaker = get_native_lang(responses)) %>%
  filter(native_speaker == "不是")

ppts_non_native_lang_M = unique(df.ppts_non_native_lang_M$subject) #2
percent_dropped = length(ppts_non_native_lang_M) / length(unique(df.resp_M$subject))
percent_dropped #0.012048

@@

ppts_en_speaker_M = unique(df.lang_en_M$subject) #66
percent_dropped = length(ppts_en_speaker_M) / length(unique(df.resp_M$subject))
percent_dropped #0.3496503 # will not use this criterion

@@

ppts_vi_speaker_M = unique(df.lang_vi_M$subject) #0
percent_dropped = length(ppts_vi_speaker_M) / length(unique(df.resp_M$subject))
percent_dropped #0

@@

ppts_lived_abroad_M = unique(df.lived_abroad_M$subject) #29
percent_dropped = length(ppts_lived_abroad_M) / length(unique(df.resp_M$subject))
percent_dropped # 0.1608392

@@

ppts_oversea_exp_M = unique(df.oversea_exp_M$subject) #8
percent_dropped = length(ppts_oversea_exp_M) / length(unique(df.resp_M$subject))
percent_dropped #0

@@

length(unique(df.resp_M$subject)) #132
```
